The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals

### 2021-01-15 publications/2020-03-paper/highlights/highlights.tex
adds highlights
Former-commit-id: d81cc9b7b4e78b95d3602c15c5d80f5297fae011
Former-commit-id: d4cf835837583cac16171310086eda753fa38615

\journal{Annals of Nuclear Energy}

@@

\begin{document}
\begin{frontmatter}
\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Five initial fissile loadings: HALEU, Pu mixed with HALEU, reactor-grade Pu, TRU, and $^{233}$U have been studied for transitioning to the thorium fuel cycle in the SD-TMSR.
	\item The MSR burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the SD-TMSR.
	\item The dynamics of $k_{eff}$, major isotopes mass, and essential safety parameters have been investigated.
	\item The neutron energy spectrum shift during the reactor operation was calculated.
	\item Temperature coefficient of reactivity evolution during SD-TMSR operation are investigated.
\end{itemize}
\end{document}

>>>>

\journal{Applied Energy}

@@

\begin{document}
\begin{frontmatter}
\title{The role of current and emerging technologies in meeting Japan's mid- to long-term carbon reduction goals}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
	\item Transition pathways using nuclear, renewables, carbon capture, and hydrogen.
	\item Includes long-term assessment up to 2100 
	\item Dynamic simulations use learning curves for cost and emissions..
	\item Sensitivity analysis identifies key parameters and thresholds.
\end{itemize}
\end{document}
